---
format: 
  pdf:
    block-headings: false
    latex_engine: xelatex
    geometry:
      - margin=0.75in
fontsize: 10pt
linkcolor: black
urlcolor: black
header-includes:
  - \usepackage{titlesec}
  - \usepackage{calligra}
  - \usepackage{tabto}
  - \usepackage{xcolor}
  - \usepackage{fontawesome5}
  - \usepackage{academicons}
  - \usepackage{fancyhdr}
  - \usepackage{fontspec}
  - \usepackage{needspace}
  - \definecolor{lightgray}{rgb}{0.52, 0.52, 0.51}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \renewcommand{\headrulewidth}{0pt}
  - \fancyfoot[C]{\thepage}
  - '\fancyfoot[R]{\footnotesize \color{lightgray} \textsc{Updated \today}}'
  - '\titleformat{\section}{\centering\huge\scshape}{\thesection}{1em}{}'
  - '\titleformat{\subsection}{\centering\Large\scshape}{\thesubsection}{1em}{}'
  - '\titleformat{\subsubsection}{\large\scshape}{\thesubsubsection}{1em}{}'
  - '\newcommand{\fn}[1]{\hfill \textsc{\small{\color{lightgray} #1}}}'
  - '\newcommand{\tabbedparagraph}[2]{\noindent#1\hspace{10pt}\begin{minipage}[t]{\dimexpr\linewidth-55pt}#2\end{minipage}\\[1em]}'
---

```{r, echo = FALSE}
unfunded <- 0
```

# Curriculum Vitae
\vspace{-0.8cm}
\begin{center}
{\Huge {\calligra Lucy}}\hspace{0.2cm}{\Large \textbf{D'Agostino McGowan, Ph.D.}}
\end{center}

\vspace{-0.5cm}

## Professional Data

::: {layout="[0.6, 0.02, 0.38]"}
::: {#first}
***Primary Appointment***  
Department of Statistical Sciences  
Wake Forest University  

\
\
***Secondary Appointment***  
Department of Biostatistics and Data Science  
Division of Public Health Sciences  
Wake Forest University School of Medicine
:::

::: {#mid}
  
:::

::: {#second}

\vspace{-1.75cm}

\faGithub \hspace{0.1cm} \href{http://github.com/LucyMcGowan}{LucyMcGowan}  
\faTwitter \hspace{0.1cm}  \href{http://twitter.com/LucyStats}{LucyStats}  
\aiOrcid \hspace{0.1cm}  \href{http://orcid.org/0000-0001-7297-9359}{0000-0001-7297-9359}  
\href{https://www.lucymcgowan.com}{www.lucymcgowan.com}  

:::

:::

```{r, echo = FALSE, warning = FALSE, message = FALSE}
googlesheets4::gs4_auth(email = "mcgowald@wfu.edu")
library("googlesheets4")
library("dplyr")
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
data <- read_sheet("1w5Fr0sKH085KmMg_XP06Nv4AdDD1cwwauxlFY0kRTTU",
                   col_types = "ccc") %>%
  arrange(label, desc(when))
```


\vspace{-0.25cm}

## Education and Training

\TabPositions{4cm}

\vspace{-.5cm}

### Degrees

\vspace{-.4cm}

**Ph.D.** in Biostatistics, May 2018 \fn{Vanderbilt University}  
*Thesis: Improving Modern Techniques of Causal Inference: Finite Sample Performance of ATM and ATO Doubly Robust Estimators, Variance Estimation for ATO Estimators, and Contextualized Tipping Point Sensitivity Analyses for Unmeasured Confounding*  

\vspace{0.1cm}

**M.S.** in Biostatistics, December 2013 \fn{Washington University in St. Louis School of Medicine}   
*Thesis: Quantitative Assessment of the Community Research Fellows Training Program*  

\vspace{0.1cm}

**B.A.** in Religious Studies and Romance Languages, May 2012 \fn{UNC Chapel Hill}  
*with Distinction and Highest Honors*

\vspace{-.5cm}

### Postdoctoral Training

\vspace{-.4cm}


**Postdoctoral Fellow**, 2018-2019 \fn{Johns Hopkins Bloomberg School of Public Health}  
Department of Biostatistics  
*Mentor: Jeffrey Leek, Ph.D.*


\vspace{-0.25cm}

## Professional Experience


```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "primary_research") %>%
  select(when, what) %>%
  mutate(
    where = purrr::map_chr(strsplit(what, "\\*\\*"), 2),
    what = stringr::str_match(what, "([^\\*]+)(?:\\*[^\\*]+){1}$")[, 2]
  ) %>%
  glue::glue_data("<when> \\tab{\\textbf{<where>}}\n\n\\vspace{-0.25cm} \\tab{\\textit{<what>}}",
                  "\n\\vspace{-0.1cm}",
                  .open = "<", .close = ">")

data %>%
  filter(label == "research", !when == "2018-2019") %>%
  select(when, what) %>%
  mutate(
    where = purrr::map_chr(strsplit(what, "\\*\\*"), 2),
    what = stringr::str_match(what, "([^\\*]+)(?:\\*[^\\*]+){1}$")[, 2]
  ) %>%
  filter(when != "2013 Summer") %>% ## Remove colditz 
  glue::glue_data("<when> \\tab{\\textbf{<where>}}\n\n\\vspace{-0.25cm} \\tab{\\textit{<what>}}",
                  "\n\\vspace{-.1cm}",
                  .open = "<", .close = ">")
```

\TabPositions{4cm}

## Publications


```{r, echo = FALSE, message = FALSE, warning = FALSE}
pubs <- read_sheet("1HPQDH3tOXtZb1DV--8wR9CKAzUz5aywWc2vM3OQ5SrU", col_types = "c") %>%
  arrange(type, desc(year))
```

+Indicates equal contributions.  
\* Indicates student advisee.

### Journal Articles (Peer-reviewed)


```{r, echo = FALSE, results = "asis", message = FALSE, warning = FALSE}
options(width = 500)
papers <- pubs %>%
  filter(type == "article", pub_type == 2) %>%
  arrange(desc(date))

writeLines(glue::glue_collapse(papers$bib, sep = "\n\n"),
           con = "lucy.bib"
)


format_dois <- function(text) {
  pattern <- "doi:(10\\.\\d{4,9}/[-._;()/:A-Za-z0-9]+)\\s*<https://doi\\.org/(10\\.\\d{4,9}/[-._;()/:A-Za-z0-9]+)>"
  replacement <- "[doi:\\1](https://doi.org/\\2)"
  formatted_text <- stringr::str_replace_all(text, pattern, replacement)
  return(formatted_text)
}

bib_content <- bibtex::read.bib("lucy.bib") %>%
  capture.output() %>%
  paste(collapse = "\n") %>%  
  stringr::str_replace_all("’", "'") %>%
  stringr::str_replace_all("D'Agostino McGowan L", "**D'Agostino McGowan L**") %>%
  stringr::str_replace_all("Mendoza H", "Mendoza H\\\\*") %>%
  stringr::str_replace_all("“", "``") %>%
  format_dois() %>%
  stringr::str_split("\n") %>%  
  unlist()

bib_content <- ifelse(bib_content == "", "\n\n 1.", bib_content) %>%
  unlist() %>%
  c("1.", .)

cat(bib_content, sep = "\n")

```

### Refereed Commentaries, Editorials, and Other Publications 

```{r, echo = FALSE, results = "asis", message = FALSE, warning = FALSE}
other_papers <- pubs %>%
  filter(type == "article", pub_type == 3) %>%
  arrange(desc(date))

writeLines(glue::glue_collapse(other_papers$bib, sep = "\n\n"),
           con = "lucy-other.bib"
)

bibtex::read.bib("lucy-other.bib") %>%
  capture.output() %>%
  paste(collapse = "\n") %>%  
  stringr::str_replace_all("’", "'") %>% 
  stringr::str_replace_all("D'Agostino McGowan L", "**D'Agostino McGowan L**") %>%
  stringr::str_replace_all("Mendoza H", "Mendoza H\\\\*") %>%
  stringr::str_replace_all("“", "``") %>%
  format_dois() %>%
  stringr::str_split("\n") %>%  
  unlist() %>% 
  ifelse(. == "", "\n\n 1.", .) %>%
  unlist() %>%
  c(glue::glue("{nrow(papers) + 1}."), .) %>%
  cat(sep = "\n")
```


<!-- ## Pre-prints -->

<!-- ```{r, echo = FALSE, results = "asis", message = FALSE, warning = FALSE} -->
<!-- options(width = 500) -->
<!-- papers <- pubs %>% -->
<!--   filter(type == "preprint") %>% -->
<!--   arrange(desc(date)) -->

<!-- writeLines(glue::glue_collapse(papers$bib, sep = "\n\n"), -->
<!--            con = "lucy-preprint.bib" -->
<!-- ) -->

<!-- bibtex::read.bib("lucy-preprint.bib") %>% -->
<!--   capture.output() %>% -->
<!--   stringr::str_replace_all("’", "'") %>% -->
<!--   stringr::str_replace_all("D'Agostino McGowan L", "**D'Agostino McGowan L**") %>% -->
<!--   stringr::str_replace_all("“", "``") %>% -->
<!--   ifelse(. == "", "\n\n 1.", .) %>% -->
<!--   unlist() %>% -->
<!--   c("1.", .) %>% -->
<!--   cat() -->
<!-- ``` -->


## Presentations

### \underline{Invited Presentations at Scientific Meetings}

```{r, echo = FALSE, message = FALSE, warning = FALSE}
presentations <- read_sheet("1-PItelqpv0Sb_LdiEDqb8O3D_Roii5nVTL07IRVbRtA",
                            col_types = "cccccdddccclcccccc") %>%
  arrange(invited, desc(start)) %>%
  mutate(title = gsub("\\&", "\\\\&", title))
```

```{r, results = "asis", message = FALSE, warning = FALSE, echo = FALSE}
presentations %>%
  filter(invited == 1 & !(what %in% c("Workshop", "Panel")), type == "conference") %>%
  glue::glue_data("\\par
\\needspace{4\\baselineskip}**<where>** \\fn{<what>}",
"\\begin{quote}<gsub('\\\\*', '', who)>, ",
"\\href{<ifelse(is.na(link), slides, link)>}{``<title>.\"}\\end{quote}",
.open = "<", .close = ">")
```

### \underline{Invited Seminars and Colloquia}

```{r, results = "asis", message = FALSE, warning = FALSE, echo = FALSE}
presentations %>%
  filter(invited == 1 & !(what %in% c("Workshop", "Panel")), type == "seminar") %>%
  glue::glue_data("\\par
\\needspace{4\\baselineskip}**<where>**",
"\\begin{quote}\\href{<ifelse(is.na(link), slides, link)>}{``<title>.\"}\\end{quote}",
.open = "<", .close = ">")
```


### \underline{Invited Workshops and Panels}

```{r, results = "asis", message = FALSE, warning = FALSE, echo = FALSE}
presentations %>%
  filter(what %in% c("Workshop", "Panel", "Lecture")) %>%
  arrange(desc(start)) %>%
  glue::glue_data("\\par
\\needspace{4\\baselineskip}**<where>** \\fn{<what>}",
"\\begin{quote}<gsub('\\\\*', '', who)>, ",
"{``<title>.\"}\\end{quote}",
.open = "<", .close = ">")
```

### \underline{Contributed Presentations at Scientific Meetings}

```{r, results = "asis", echo = FALSE}
presentations %>%
  filter(invited == 0 & !(what %in% c("Workshop", "Panel"))) %>% 
  glue::glue_data("\\par
\\needspace{4\\baselineskip}**<where>** \\fn{<what>}",
"\\begin{quote}<gsub('\\\\*', '', who)>, ",
"\\href{<link>}{``<title>.\"}\\end{quote}",
.open = "<", .close = ">")
```


## Grant Funding

\vspace{-0.5cm}

### Current

```{r, echo = FALSE, results = "asis"}
funding <- read_sheet("1p0SFLMgcfxW4EqPNYCAlkgZzh872ZfOkPK8IPZBVK9Q") %>%
  arrange(-start)
funding %>%
  filter(funded == "yes", current == "yes") %>%
  glue::glue_data("\\tabbedparagraph{<start><ifelse(!is.na(end), glue::glue('-{end}'), '     ')>}{<funder>, \\textit{<what>}<ifelse(!is.na(PI), glue::glue(' (PI: {PI})'), '')>\\\\ Role: <role>  <ifelse(!is.na(amount), glue::glue('({amount})'), '')>} \n\n",
                  .open = "<", .close = ">")
```

\vspace{-0.75cm}

### Completed

```{r, echo = FALSE, results = "asis"}
funding %>%
  filter(funded == "yes", current == "no") %>%
  glue::glue_data("\\tabbedparagraph{<start><ifelse(!is.na(end), glue::glue('-{end}'), '\\\\hspace{0.8cm}')>}{<funder>, \\textit{<what>}<ifelse(!is.na(PI), glue::glue(' (PI: {PI})'), '')>\\\\ Role: <role>  <ifelse(!is.na(amount), glue::glue('({amount})'), '')>} \n\n",
                  .open = "<", .close = ">")
```

\vspace{-0.75cm}

### Pending


```{r, echo = FALSE, results = "asis"}
funding %>%
 filter(funded == "pending") %>%
  glue::glue_data("\\tabbedparagraph{<start><ifelse(!is.na(end), glue::glue('-{end}'), '\\\\hspace{0.8cm}')>}{<funder>, \\textit{<what>}<ifelse(!is.na(PI), glue::glue(' (PI: {PI})'), '')>\\\\ Role: <role>  <ifelse(!is.na(amount), glue::glue('({amount})'), '')>} \n\n",
                  .open = "<", .close = ">")

```

```{r, echo = FALSE, results = "asis"}
if (unfunded) {
  glue::glue("## Grants (unfunded)")
}
```

```{r, echo = FALSE, results = "asis"}
if (unfunded) {
  funding %>%
    filter(funded == "no") %>%
    glue::glue_data("\\textbf{<start>}\\vspace{-0.65cm} \\begin{quote} \\textit{<funder>} \\newline Role: <role> \\newline<what>\\end{quote}",
                    .open = "<", .close = ">")
}
```

\vspace{-0.5cm}

## Software

```{r, echo = FALSE}
software <- pubs %>%
  filter(type == "software") %>%
  arrange(desc(year))

software_cite <- function(x) {
  glue::glue_data(x, "[**{title}**]({link}): {description} ({year})\n\n\n")
}
```

\vspace{-0.5cm}

### Author & Maintainer 

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "maintainer") %>%
  software_cite()
```


### Author

\* Indicates package is maintained by former student advisee

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "author") %>%
  software_cite()
```

### Contributer

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "contributer") %>%
  software_cite()
```

## Teaching Experience

### Wake Forest University

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "teaching_wfu") %>%
  arrange(desc(when), what) %>%
  glue::glue_data("* {what} ({when})")
```

### Vanderbilt University

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "teaching_vandy") %>%
  glue::glue_data("* {what} ({when})")
```

### Washington University in St. Louis

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "teaching_wustl") %>%
  glue::glue_data("* {what} ({when})")
```

### Online Courses

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "teaching_online") %>%
  glue::glue_data("* {what} ({when})")
```

## Student Engagement

### Undergraduate Theses

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "undergrad_thesis") %>%
  glue::glue_data("* {what} ({when})")
```

### Independent Studies

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "undergrad_ind_study") %>%
  arrange(desc(when)) %>%
  glue::glue_data("* {what} ({when})")
```

### Committees

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "committee") %>%
  mutate(what = glue::glue("{what}")) %>%
  pull(what) %>%
  glue::glue_collapse(", ", last = " and ")
```


## Awards

\TabPositions{2cm}

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "awards") %>%
  select(when, what) %>%
  mutate(
    link = case_when(
      grepl("\\[", what) ~ gsub('\\(|\\)|\\[.*\\]','', what),
      TRUE ~ ""
    ),
    title = case_when(
      grepl("\\[", what) ~ gsub('\\[|\\]|\\(.*\\)','',what),
      TRUE ~ ""
    ),
    what = case_when(
      grepl("\\[", what) ~ glue::glue("\\href{<link>}",
                                      "{<title>}",
                                      .open = "<", .close = ">" ),
      TRUE ~ what
    )
  ) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")
```


## Professional Activities

### Internal Service

***Department of Statistical Sciences***


```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "wfu_service_dept") %>%
  select(when, what) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")

```

***College-wide***


```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "wfu_service_college") %>%
  select(when, what) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")

```

### External Professional Service


```{r, echo = FALSE, results = "asis"}
prof_service <- data %>%
  filter(label == "professional_service") %>%
  select(when, what) %>%
  mutate(asa = grepl(" ASA ", what),
         editor = grepl("Editor", what),
         enar = grepl("ENAR", what)
  )

prof_service %>%
  filter(!asa, !editor, !enar) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")

```

***Service on Editorial Boards***

```{r, echo = FALSE, results = "asis"}
prof_service %>%
  filter(editor) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")

```

***Service for the American Statistical Association***


```{r, echo = FALSE, results = "asis"}
prof_service %>%
  filter(asa) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")

```

***Service for the International Biometric Society (ENAR)***


```{r, echo = FALSE, results = "asis"}
prof_service %>%
  filter(enar) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")

```


***Referee***

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "referee") %>%
  mutate(what = glue::glue("*{what}*")) %>%
  pull(what) %>%
  glue::glue_collapse(", ", last = " and ")
```

***Chaired Conference Sessions***

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "chair") %>%
  select(when, what) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")
```

## Outreach


```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "outreach") %>%
  select(when, what) %>%
  mutate(
    link = case_when(
      grepl("\\[", what) ~ gsub('\\(|\\)|\\[.*\\]','', what),
      TRUE ~ ""
    ),
    title = case_when(
      grepl("\\[", what) ~ gsub('\\[|\\]|\\(.*\\)','',what),
      TRUE ~ ""
    ),
    what = case_when(
      grepl("\\[", what) ~ glue::glue("\\href{<link>}",
                                      "{<title>}",
                                      .open = "<", .close = ">" ),
      TRUE ~ what
    )
  ) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")
```

## Press

```{r, echo = FALSE, results = "asis"}
pubs %>%
  filter(type == "press") %>%
  arrange(desc(year)) %>%
  glue::glue_data("**<title>** (<year>) \\textit{<publication>}. (<description>). ",
                  "Available at: ",
                  "\\url{<link>}\n\n\\vspace{0.5cm}", 
                  .open = "<", .close = ">")
```

