---
output: 
  pdf_document:
    latex_engine: xelatex
fontsize: 12pt
geometry: margin=0.55in
subparagraph: yes
header-includes:
  - \usepackage{titlesec}
  - \usepackage{calligra}
  - \usepackage{tabto}
  - \usepackage{xcolor}
  - \usepackage{fontawesome}
  - \usepackage{academicons}
  - \usepackage{fancyhdr}
  - \definecolor{lightgray}{HTML}{999999}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \renewcommand{\headrulewidth}{0pt}
  - \fancyfoot[C]{\thepage}
  - '\fancyfoot[R]{\footnotesize \color{lightgray} \textsc{Updated \today}}'
  - '\titleformat{\subsection}{\centering\Large\scshape}{\thesubsection}{1em}{}'
  - '\newcommand{\fn}[1]{\hfill \textsc{\small{\color{lightgray} #1}}}'
---

\begin{center}
{\Huge {\calligra Lucy}}\hspace{0.1cm}{\Large \textbf{D'Agostino McGowan}}

\href{https://www.lucymcgowan.com}{www.lucymcgowan.com}

\faGithub \hspace{0.1cm} \href{http://github.com/LucyMcGowan}{LucyMcGowan} \hspace{0.1cm}\faTwitter \hspace{0.1cm}  \href{http://twitter.com/LucyStats}{LucyStats} \hspace{0.1cm} \aiOrcid \hspace{0.1cm}  \href{http://orcid.org/0000-0001-7297-9359}{0000-0001-7297-9359}
\end{center}

**defining attributes**
*goal-driven leadership, advanced analytic skills, strategic thinking, resourceful team player, sunny disposition, public speaking, organizational & communication skills*
<!-- ## Interests -->

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library("googlesheets")
library("dplyr")
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
data <- gs_url("https://docs.google.com/spreadsheets/d/1w5Fr0sKH085KmMg_XP06Nv4AdDD1cwwauxlFY0kRTTU/edit#gid=0", lookup = TRUE, verbose = FALSE) %>%
  gs_read(verbose = FALSE) %>%
  arrange(label, desc(when))
```

<!-- ```{r, echo = FALSE, results = "asis"} -->
<!-- interests <- data %>% -->
<!--   filter(label == "interests") %>% -->
<!--   select(what) -->
<!-- cat(paste(interests$what, collapse = ", ")) -->
<!-- ``` -->

## Education

**PhD** in Biostatistics, May 2018, GPA 3.95 \fn{Vanderbilt University}  
*Thesis: Improving Modern Techniques of Causal Inference: Finite Sample Performance of ATM and ATO Doubly Robust Estimators, Variance Estimation for ATO Estimators, and Contextualized Tipping Point Sensitivity Analyses for Unmeasured Confounding*  

\vspace{0.25cm}

**MS** in Biostatistics, December 2013, GPA 3.88 \fn{Washington University School of Medicine}   
*Thesis: Quantitative Assessment of the Community Research Fellows Training Program*  

\vspace{0.25cm}

**BA** with Distinction and Highest Honors\fn{University of North Carolina at Chapel Hill}  
Religious Studies: GPA 3.92 Romance Languages: GPA 3.86


## Research Experience

\TabPositions{4cm}


```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "research") %>%
  select(when, what) %>%
  mutate(
    where = purrr::map_chr(strsplit(what, "\\*\\*"), 2),
    what = stringr::str_match(what, "([^\\*]+)(?:\\*[^\\*]+){1}$")[, 2]
  ) %>%
  glue::glue_data("<when> \\tab{\\textbf{<where>}}\n\n\\vspace{-0.25cm} \\tab{\\textit{<what>}}",
                  "\n\n\n\\vspace{0.25cm}",
                  .open = "<", .close = ">")
```

## Programming

**Develop:** R  
**Use:** R, SAS, Stata, Python, ArcGIS

## Awards

\TabPositions{2cm}

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "awards") %>%
  select(when, what) %>%
  mutate(
    link = case_when(
      grepl("\\[", what) ~ gsub('\\(|\\)|\\[.*\\]','', what),
      TRUE ~ ""
    ),
    title = case_when(
      grepl("\\[", what) ~ gsub('\\[|\\]|\\(.*\\)','',what),
      TRUE ~ ""
    ),
    what = case_when(
      grepl("\\[", what) ~ glue::glue("\\href{<link>}",
                                      "{<title>}",
                                      .open = "<", .close = ">" ),
      TRUE ~ what
    )
  ) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")
```

## Outreach

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "outreach") %>%
  select(when, what) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")
```

## Professional Activities

#### Professional Service

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "professional_service") %>%
  select(when, what) %>%
  glue::glue_data("<when> \\tab{<what>} \n\n\n",
                  .open = "<", .close = ">")

```


#### Referee

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "referee") %>%
  glue::glue_data("* {what}")
```

## Teaching Experience

#### Vanderbilt University

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "teaching_vandy") %>%
  glue::glue_data("* {what} ({when})")
```

#### Washington University in St. Louis

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "teaching_wustl") %>%
  glue::glue_data("* {what} ({when})")
```

### Online Courses

```{r, echo = FALSE, results = "asis"}
data %>%
  filter(label == "teaching_online") %>%
  glue::glue_data("* {what} ({when})  ")
```

## Invited Presentations

```{r, echo = FALSE, message = FALSE, warning = FALSE}
presentations <- gs_url("https://docs.google.com/spreadsheets/d/1-PItelqpv0Sb_LdiEDqb8O3D_Roii5nVTL07IRVbRtA/edit#gid=0", verbose = FALSE) %>%
  gs_read(verbose = FALSE) %>%
  arrange(invited, desc(when))
```

```{r, results = "asis", message = FALSE, warning = FALSE, echo = FALSE}
presentations %>%
  filter(invited == 1) %>%
  glue::glue_data("**<where>** \\fn{<what>} \\vspace{-0.65cm}",
                  "\\begin{quote}<gsub('\\\\*', '', who)>,",
                  "\\href{<link>}{\"<title>.\"}\\end{quote}",
                  .open = "<", .close = ">")
```

## Contributed Presentations

```{r, results = "asis", echo = FALSE}
presentations %>%
  filter(invited == 0) %>% 
  glue::glue_data("**<where>** \\fn{<what>} \\vspace{-0.5cm}",
                  "\\begin{quote}<gsub('\\\\*', '', who)>,",
                  "\\href{<link>}{\"<title>.\"}\\end{quote}",
                  .open = "<", .close = ">")
```

## Software

```{r, echo = FALSE, message = FALSE, warning = FALSE}
pubs <- gs_url("https://docs.google.com/spreadsheets/d/1HPQDH3tOXtZb1DV--8wR9CKAzUz5aywWc2vM3OQ5SrU/edit#gid=0", verbose = FALSE) %>%
  gs_read(verbose = FALSE) %>%
  arrange(type, desc(year))
```

```{r, echo = FALSE}
software <- pubs %>%
  filter(type == "software")

software_cite <- function(x) {
  glue::glue_data(x, "[**{title}**]({link}): {description} \n\n\n")
}
```

#### Author & Maintainer

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "maintainer") %>%
  software_cite()
```

#### Author

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "author") %>%
  software_cite()
```

#### Contributer

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "contributer") %>%
  software_cite()
```

## Peer-reviewed Publications

```{r, results = "asis", echo = FALSE}
papers <- pubs %>%
  filter(pub_type == "2")

glue::glue_data(papers, "1. {authors} ({year}). {title}. *{publication}, {volume}*({number}), {pages}.\n\n\n")
```


