---
output: 
  html_document:
    css: style.css
---

<h1><span style="font-family:myFancyFont; font-size:3em;">Lucy</span> D'Agostino McGowan</h1> <br>

<div class="prettycol">
  <div class="column sidebar">
**contact**  
2525 West End 11000
Nashville, TN 37203

**website**  
[lucymcgowan.com](http://lucymcgowan.com)

**twitter**  
[LucyStats](http://twitter.com/LucyStats)

**github**  
[LucyMcGowan](http://github.com/LucyMcGowan)

**orcid**  
[0000-0001-7297-9359](http://orcid.org/0000-0001-7297-9359)

**jump to section**

<a href="#interests">Interests</a>  
<a href="#education">Education</a>  
<a href="#research">Research Experience</a>  
<a href="#awards">Awards</a>  
<a href="#outreach">Outreach</a>  
<a href="#invited">Invited Presentations</a>  
<a href="#contributed">Contributed Presentations</a>  
<a href="#software">Software</a>  
<a href="#pubs">Peer-reviewed Publications</a>  

**languages**  
proficient Italian literary,
written, & oral skills

**programming**  
**dev:** R **use:** R, SAS,
Stata, Python, ArcGIS

**defining attributes**
goal-driven leadership,
advanced analytic skills,
strategic thinking,
resourceful team player,
sunny disposition `r emo::ji("sunflower")`,
public speaking,
organizational &
communication skills

</div>
<h2 id="interests"> <span style='color:#26D1EA'>Int</span>erests </h2>

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library("googlesheets")
library("dplyr")
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
data <- gs_url("https://docs.google.com/spreadsheets/d/1w5Fr0sKH085KmMg_XP06Nv4AdDD1cwwauxlFY0kRTTU/edit#gid=0", verbose = FALSE) %>%
  gs_read(verbose = FALSE) %>%
  arrange(label, desc(when))
```

```{r, echo = FALSE, results = "asis"}
interests <- data %>%
  filter(label == "interests") %>%
  select(what)
cat(paste(interests$what, collapse = ", "))
```

<h2 id="education"><span style='color:#C2E15F'>Edu</span>cation </h2>
<span class='right' style='color:gray'>Vanderbilt University</span>
**PhD** Student in Biostatistics, GPA 3.95 

<span class='right' style='color:gray'>Washington University School of Medicine</span>
**MS** in Biostatistics, December 2013, GPA 3.88   <br>
*Thesis: Quantitative Assessment of the Community Research Fellows Training Program*

<span class='right' style='color:gray'> University of North Carolina at Chapel Hill</span>
**BA** with Distinction and Highest Honors   <br>
Religious Studies: GPA 3.92 Romance Languages: GPA 3.86


<h2 id="research"><span style='color:#FDA333'>Res</span>earch Experience </h2>

```{r, echo = FALSE}
research <- data %>%
  filter(label == "research") %>%
  select(when, what)
htmlTable::htmlTable(research, 
                     header = c(NA,NA) ,
                     rnames = FALSE,
                     align = "ll",
                     css.cell = "padding-left: .5em; padding-right: .2em;")
```

<h2 id="awards"> <span style='color:#D3A4F9'>Awa</span>rds</h2>

```{r, echo = FALSE}
awards <- data %>%
  filter(label == "awards") %>%
  select(when, what)
htmlTable::htmlTable(awards, 
                     header = c(NA,NA) ,
                     rnames = FALSE,
                     align = "ll",
                     css.cell = "padding-left: .5em; padding-right: .2em;")
```

<h2 id="outreach"> <span style='color:#FB4485'>Out</span>reach</h2>

```{r, echo = FALSE}
outreach <- data %>%
  filter(label == "outreach") %>%
  select(when, what)
htmlTable::htmlTable(outreach, 
                     header = c(NA,NA) ,
                     rnames = FALSE,
                     align = "ll",
                     css.cell = "padding-left: .5em; padding-right: .2em;")
```

<h2 id="invited"> <span style='color:#26D1EA'>Sel</span>ect Invited Presentations</h2>

```{r, echo = FALSE, message = FALSE, warning = FALSE}
presentations <- gs_url("https://docs.google.com/spreadsheets/d/1-PItelqpv0Sb_LdiEDqb8O3D_Roii5nVTL07IRVbRtA/edit#gid=0", verbose = FALSE) %>%
  gs_read(verbose = FALSE) %>%
  arrange(invited, desc(when))
```

```{r, results = "asis", echo = FALSE}
invited <- presentations %>%
  filter(invited == 1)

glue::glue_data(invited, "<span class='right' style='color:gray'> {what} </span> <span class'left'>**{where}**</span> <br> <blockquote> {who}, [\"{title}.\"]({link}) </blockquote>")
```

<h2 id="contributed"> <span style='color:#C2E15F'>Con</span>tributed Presentations </h2>

```{r, results = "asis", echo = FALSE}
contrib <- presentations %>%
  filter(invited == 0)

glue::glue_data(contrib, "<span class='right' style='color:gray'> {what} </span> <span class'left'>**{where}**</span> <br> <blockquote> {who}, [\"{title}.\"]({link}) </blockquote>")
```

<h2 id="software"><span style='color:#FDA333'>Sof</span>tware</h2>

```{r, echo = FALSE, message = FALSE, warning = FALSE}
pubs <- gs_url("https://docs.google.com/spreadsheets/d/1HPQDH3tOXtZb1DV--8wR9CKAzUz5aywWc2vM3OQ5SrU/edit#gid=0", verbose = FALSE) %>%
  gs_read(verbose = FALSE) %>%
  arrange(type, desc(year))
```

```{r, echo = FALSE}
software <- pubs %>%
  filter(type == "software")

software_cite <- function(x) {
  glue::glue_data(x, "[**{title}**]({link}): {description} <br><br>")
}
```

#### Author & Maintainer

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "maintainer") %>%
  software_cite()
```

#### Author

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "author") %>%
  software_cite()
```

#### Contributer

```{r, results = "asis", echo = FALSE}
software %>%
  filter(authors == "contributer") %>%
  software_cite()
```

<h2 id="pubs"><span style='color:#D3A4F9'>Peer</span>-reviewed Publications</h2>

```{r, results = "asis", echo = FALSE}
papers <- pubs %>%
  filter(type == "article")

glue::glue_data(papers, "{authors} ({year}). {title}. *{publication}, {volume}*({number}), {pages}. <br><br>")
```

</div>